Imaging of cortical oxygen tension and blood flow following targeted photothrombotic stroke

### 2018-06-14 article.tex
Highlighted changes in the text

\documentclass[12pt]{spieman}  % 12pt font required by SPIE;
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{array}
\usepackage{lineno}

@@

The emitted phosphorescence was separated from the excitation light and LSCI laser using a pair of dichroic beamsplitters (650 nm, ZT640rdc, Chroma Technology and 750 nm, FF750-SDi02, Semrock) and a bandpass filter (775$\pm$26 nm, 84-106, Edmund Optics) and relayed to a photomultiplier tube for detection (H7422P-50, Hamamatsu Photonics). The analog signal was amplified (C9999, Hamamatsu Photonics), digitized at 100 MHz, and accumulated by the FPGA for averaging, after which it was transferred to the host computer and written to file. The maximum pattern projection rate and temporal resolution of the \pO\ measurements were limited by the strength of the phosphorescent signal. The projected pattern size, dye concentration, and excitation laser power all influenced the resulting signal intensity and the necessary averaging of phosphorescent decays. In order to balance the signal-to-noise ratio and speed, patterns were displayed at 10 Hz with 200 decays collected during each projection. While faster pattern rates were possible (e.g. 50 Hz with 40 decays averaged), the reduction in averaging negatively affected the quality of the recorded decays.

@@

\subsection{Targeted Photothrombosis}
The DMD was also used to induce arbitrarily-shaped photothrombotic occlusions in the cortical vasculature using rose bengal. Rose bengal is a fast-clearing photothrombotic agent that photochemically triggers localized clot formation upon irradiation with green light \cite{Watson:1985bp,Klaassen:1976kg,Wilson:1991tv}. An additional 532 nm laser (200 mW, AixiZ) was coaligned with the two modulated lasers and relayed to the DMD. Structured illumination with the DMD allows for the selective targeting of individual vessels for occlusion while minimizing exposure in the surrounding parenchyma. Rose bengal was injected intravenously (50 $\mu$L, 15 mg/mL) and the target vessels exposed to DMD-patterned green light for 5 - 10 minutes. Descending arterioles were the primary targets because they serve as bottlenecks in the cortical oxygen supply \cite{Nishimura:2007hk}. Oxygen tension measurements were restricted when performing photothrombosis to the region being targeted for occlusion. LSCI was used to monitor clot formation within the targeted area and control the progression of the occlusion.

@@

\subsection{Excitation Wavelength Dependence of Measured Oxygen Tension}
Static oxygen tension measurements in the vasculature of the mouse cortex are shown in Fig. 3. Five different regions including two arterioles, two veins, and an area of unresolvable vasculature (parenchyma) were targeted for selective illumination using both the 445 nm and 637 nm excitation lasers (Fig.~\ref{fig:static_oxygen}a). The measured \pO\ within each region aligns well with physiological expectations as both arterioles have higher \pO\ than the venous or parenchymal areas (Fig.~\ref{fig:static_oxygen}b). The effects of wavelength can be seen as 445 nm excitation resulted in a broader range of oxygen tension values (48 - 83 mmHg) compared to 637 nm excitation (75 - 82 mmHg). Despite differences in absolute value, the trend of arterioles having greater \pO\ than parenchyma, which in turn has greater \pO\ than veins, exists for both excitation wavelengths. As shown previously in Fig.~\ref{fig:oxyphor_ptg4}d, no differences in \pO\ were observed between the two wavelengths in cuvette samples.

@@

The chronic progression of the ischemia was tracked for eight days following photothrombosis. The perfusion of the occluded arteriole and broader effect on cortical flow was tracked using LSCI as shown in Fig.~\ref{fig:chronic}a. Tiled \pO\ maps acquired using both 445 nm and 637 nm excitation (Fig.~\ref{fig:chronic}b, c) reveal the spatial extent of the oxygen deficit, including a large gradient between the occluded vessel and the surrounding tissue on Days +1 and +2. The same five regions used during photothrombosis were targeted for chronic relative blood flow and \pO\ measurements (Fig.~\ref{fig:chronic}d-f). Relative blood flow was calculated using the pre-stroke (Day -0) measurements as baseline.

@@

The comparison of excitation wavelengths revealed significant differences in measured oxygen tension. Static \pO\ measurements under 445 nm illumination spanned a range five times larger than that of 637 nm illumination. This discrepancy was most noticeable in venous regions, with the shorter excitation wavelength resulting in \pO\ values around 50 mmHg whereas the longer wavelength resulted in values around 75 mmHg. Since depth penetration is heavily dependent upon wavelength\cite{Deng:2003kb}, the difference is likely the result of photons sampling a much larger volume of tissue under 637 nm illumination. An estimate of transmission through a surface vessel at both wavelengths can be obtained using the Beer-Lambert Law. Because scattering increases the distance traveled by photons in tissue, this represents the most conservative estimate of the effect of wavelength on transmission. Assuming hemoglobin is the primary absorber in blood plasma with a concentration of 2.3 mM \cite{Robles:2010cw} and 95\% SaO$_{2}$, the transmittance at 445 nm and 637 nm through a 100 $\mu$m arteriole is 0.9\% and 96.5\%, respectively. As excitation wavelength approaches the tissue optical window, the transmission of incident light significantly increases. The 445 nm light is almost entirely confined within a vessel of that caliber and does not extensively sample deeper microvasculature. Because the 637 nm light penetrates further into the brain, the measured \pO\ is skewed away from the vascular value and is more representative of a bulk volumetric average. This is consistent with prior Monte Carlo modeling that found fluorescence primarily originates from within large surface vasculature at shorter wavelengths \cite{Davis:2011wj}. As excitation wavelength increases, a larger fraction of the detected fluoresecence originates from beyond the vessel.

@@

The chronic measurements revealed a severe post-stroke blood flow and oxygen deficit that recovered almost completely within five days. The spatial extent of the ischemia can be clearly seen on Days +1 and +2 in both the speckle contrast imagery and tiled \pO\ maps in Fig.~\ref{fig:chronic}. The large gradient between the occluded vessel and surrounding tissue resembles the ischemic penumbra that the photothrombotic technique rarely produces \cite{Carmichael:2005gk}. By patterning illumination light instead of irradiating a circular region, the photothrombosis is contained within the targeted vessel, which allows the infarct to manifest downstream of the occlusion. By Day +5, the targeted vessel appeared to have fully reperfused and there was no evidence of hypoxia in the tiled \pO\ measurements. The speed of this recovery is faster than previously reported \cite{Schrandt:2015gu}, but can likely be explained by the smaller area targeted for photothrombosis, which resulted in a less severe ischemic lesion.

>>>>

\documentclass[12pt]{spieman}  % 12pt font required by SPIE;
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{array}
\usepackage{lineno}
\usepackage{xcolor}

@@

The emitted phosphorescence was separated from the excitation light and LSCI laser using a pair of dichroic beamsplitters (650 nm, ZT640rdc, Chroma Technology and 750 nm, FF750-SDi02, Semrock) and a bandpass filter (775$\pm$26 nm, 84-106, Edmund Optics) and relayed to a photomultiplier tube for detection (H7422P-50, Hamamatsu Photonics). The analog signal was amplified (C9999, Hamamatsu Photonics), digitized at 100 MHz, and accumulated by the FPGA for averaging, after which it was transferred to the host computer and written to file. \textcolor{red}{The maximum pattern projection rate and temporal resolution of the \pO\ measurements were limited by the strength of the phosphorescent signal. The projected pattern size, dye concentration, and excitation laser power all influenced the resulting signal intensity and the necessary averaging of phosphorescent decays.} In order to balance the signal-to-noise ratio and speed, patterns were displayed at 10 Hz with 200 decays collected during each projection. While faster pattern rates were possible (e.g. 50 Hz with 40 decays averaged), the reduction in averaging negatively affected the quality of the recorded decays.

@@

\subsection{Targeted Photothrombosis}
The DMD was also used to induce arbitrarily-shaped photothrombotic occlusions in the cortical vasculature using rose bengal. Rose bengal is a fast-clearing photothrombotic agent that photochemically triggers localized clot formation upon irradiation with green light \cite{Watson:1985bp,Klaassen:1976kg,Wilson:1991tv}. \textcolor{red}{An additional 532 nm laser (200 mW, AixiZ) was coaligned with the two modulated lasers and relayed to the DMD.} Structured illumination with the DMD allows for the selective targeting of individual vessels for occlusion while minimizing exposure in the surrounding parenchyma. Rose bengal was injected intravenously (50 $\mu$L, 15 mg/mL) and the target vessels exposed to DMD-patterned green light for 5 - 10 minutes. Descending arterioles were the primary targets because they serve as bottlenecks in the cortical oxygen supply \cite{Nishimura:2007hk}. Oxygen tension measurements were restricted when performing photothrombosis to the region being targeted for occlusion. LSCI was used to monitor clot formation within the targeted area and control the progression of the occlusion.

@@

\subsection{Excitation Wavelength Dependence of Measured Oxygen Tension}
Static oxygen tension measurements in the vasculature of the mouse cortex are shown in Fig. 3. Five different regions including two arterioles, two veins, and an area of unresolvable vasculature (parenchyma) were targeted for selective illumination using both the 445 nm and 637 nm excitation lasers (Fig.~\ref{fig:static_oxygen}a). The measured \pO\ within each region aligns well with physiological expectations as both arterioles have higher \pO\ than the venous or parenchymal areas (Fig.~\ref{fig:static_oxygen}b). The effects of wavelength can be seen as 445 nm excitation resulted in a broader range of oxygen tension values (48 - 83 mmHg) compared to 637 nm excitation (75 - 82 mmHg). \textcolor{red}{Despite differences in absolute value, the trend of arterioles having greater \pO\ than parenchyma, which in turn has greater \pO\ than veins, exists for both excitation wavelengths.} As shown previously in Fig.~\ref{fig:oxyphor_ptg4}d, no differences in \pO\ were observed between the two wavelengths in cuvette samples.

@@

The chronic progression of the ischemia was tracked for eight days following photothrombosis. The perfusion of the occluded arteriole and broader effect on cortical flow was tracked using LSCI as shown in Fig.~\ref{fig:chronic}a. \textcolor{red}{Tiled \pO\ maps acquired using both 445 nm and 637 nm excitation (Fig.~\ref{fig:chronic}b, c) reveal the spatial extent of the oxygen deficit, including a large gradient between the occluded vessel and the surrounding tissue on Days +1 and +2.} The same five regions used during photothrombosis were targeted for chronic relative blood flow and \pO\ measurements (Fig.~\ref{fig:chronic}d-f). Relative blood flow was calculated using the pre-stroke (Day -0) measurements as baseline.

@@

The comparison of excitation wavelengths revealed significant differences in measured oxygen tension. Static \pO\ measurements under 445 nm illumination spanned a range five times larger than that of 637 nm illumination. This discrepancy was most noticeable in venous regions, with the shorter excitation wavelength resulting in \pO\ values around 50 mmHg whereas the longer wavelength resulted in values around 75 mmHg. Since depth penetration is heavily dependent upon wavelength\cite{Deng:2003kb}, the difference is likely the result of photons sampling a much larger volume of tissue under 637 nm illumination. An estimate of transmission through a surface vessel at both wavelengths can be obtained using the Beer-Lambert Law. Because scattering increases the distance traveled by photons in tissue, this represents the most conservative estimate of the effect of wavelength on transmission. Assuming hemoglobin is the primary absorber in blood plasma with a concentration of 2.3 mM \cite{Robles:2010cw} and 95\% SaO$_{2}$, the transmittance at 445 nm and 637 nm through a 100 $\mu$m arteriole is 0.9\% and 96.5\%, respectively. As excitation wavelength approaches the tissue optical window, the transmission of incident light significantly increases. The 445 nm light is almost entirely confined within a vessel of that caliber and does not extensively sample deeper microvasculature. Because the 637 nm light penetrates further into the brain, the measured \pO\ is skewed away from the vascular value and is more representative of a bulk volumetric average. \textcolor{red}{This is consistent with prior Monte Carlo modeling that found fluorescence primarily originates from within large surface vasculature at shorter wavelengths \cite{Davis:2011wj}. As excitation wavelength increases, a larger fraction of the detected fluoresecence originates from beyond the vessel.}

@@

The chronic measurements revealed a severe post-stroke blood flow and oxygen deficit that recovered almost completely within five days. \textcolor{red}{The spatial extent of the ischemia can be clearly seen on Days +1 and +2 in both the speckle contrast imagery and tiled \pO\ maps in Fig.~\ref{fig:chronic}}. The large gradient between the occluded vessel and surrounding tissue resembles the ischemic penumbra that the photothrombotic technique rarely produces \cite{Carmichael:2005gk}. By patterning illumination light instead of irradiating a circular region, the photothrombosis is contained within the targeted vessel, which allows the infarct to manifest downstream of the occlusion. By Day +5, the targeted vessel appeared to have fully reperfused and there was no evidence of hypoxia in the tiled \pO\ measurements. The speed of this recovery is faster than previously reported \cite{Schrandt:2015gu}, but can likely be explained by the smaller area targeted for photothrombosis, which resulted in a less severe ischemic lesion.
